---
title: "Example Github Page"
author: "Mara Alexeev, MD, MPH"
date: "Updated `r Sys.Date()`"
---

```{r libraries, echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(kableExtra)
library(magrittr)
library(plotly)
library(sf)
```

This is a very ***basic*** static webpage you can make from an .Rmd file.

# Tiny examples

## Rmarkdown

Math expressions, e.g. $Y = X\beta + \epsilon$.

You can insert footnotes.[^1]

[^1]: A very informative footnote here.

[Make links](https://github.com/MaraAlexeev/example_for_CIC_workshop_May_2021) to important places like a Github Repository for this static webpage you are viewing.

## Tables

There are excellent ways to display tabular data.

One of my favorite resources [here](https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html#Overview).

```{r, echo=FALSE}
knitr::kable(head(iris, 10)) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

You can get [very over-the-top](https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html#Grouped_Columns__Rows) with different ways to organize the data.

```{r, echo=FALSE}
dt <- mtcars[1:5, 1:6]
knitr::kable(head(dt, 10))%>%
  kable_paper() %>%
  add_header_above(c(" ", "My Group" = 2, "My Other Group " = 2, "Another Group" = 2)) %>%
  add_header_above(c(" ", "This Group" = 4, "That Group" = 2)) %>%
  add_header_above(c(" ", "Maybe Too Many Groups" = 6))
```

## Plots

R has amazing graphing powers---my favorite is the `ggplot2` package---and a great community with people sharing their work---look up [\#TidyTuesday](https://twitter.com/hashtag/TidyTuesday?src=hashtag_click) on Twitter---and [teaching others](https://ggplot2-book.org/introduction.html) how to do great work too. The `plotly` package let's you make your [plots interactive](https://plotly.com/ggplot2/) as well. Below are some examples from the Plotly reference guide, shown first as static images and then as interactive ones.


```{r}

nc <- sf::st_read(system.file("shape/nc.shp", package = "sf"), quiet = TRUE)


nc_plot <- ggplot(data = nc) + geom_sf(aes(fill = AREA))
nc_plot
                                       
fig <- ggplotly(nc_plot)

fig
```

```{r}
set.seed(8)
dat <- data.frame(cond = factor(rep(c("Treatment","Placebo"), each=200)), happiness = c(rnorm(200),rnorm(200, mean=.8)))

p <- ggplot(dat, aes(x=cond, y=happiness, fill=cond)) + geom_boxplot()

p

fig <- ggplotly(p)

fig
```


```{r}
df <- diamonds[sample(1:nrow(diamonds), size = 1000),]

p <- ggplot(df, aes(x = color)) + 
  geom_bar(aes(y = ..count../sum(..count..), fill = cut)) + 
  scale_fill_brewer(palette = "Set3") + 
  ylab("Percent") + 
  ggtitle("Show precentages in bar chart") +
  labs(x = "Color")

p

fig <- ggplotly(p)

fig
```

